---
title: "Natively-Entangled-Proteins-Linked-to-Human-Disease"
output:
  html_document:
    toc: false
    toc_depth: 3
    number_sections: false
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, echo=FALSE, results='asis'}
cat('
<style>
body {
  font-family: "Times New Roman", Times, serif !important;
  text-align: justify;
}

p {
  text-align: justify;
}

h1, h2, h3, h4, h5, h6 {
  font-family: "Times New Roman", Times, serif !important;
}

code, pre {
  font-family: "Times New Roman", Times, serif !important;
}
</style>
')
```

# Overview

This repository contains the code needed to reproduce the results in [PAPER PLACEHOLDER].

Because many source data files are very large, this repository contains code and instructions to run the analyses, but does not include all raw data by default. To recreate the full datasets used in the paper, please contact [CONTACT NAME / EMAIL] to obtain the raw data bundle and place it in the appropriate directories described below.


## Repository structure

The repository is organized into the following folders:

- `AnalysisCodes/`: analysis scripts organized by section
- `Data/`: input data files
- `DataExtractionCode/`: scripts for pulling/assembling raw data into analysis-ready formats
- `Execute/`: wrappers or “run-all” scripts to execute analyses end-to-end
- `Functions/`: shared functions used across scripts (cleaning)
- `Log/`: run logs and timestamps
- `Results/`: generated outputs (tables/figures)

Each folder contains its own README describing what belongs there and how to use it.


### Quick start R scripts for running analyses:

- `Execute/RunAll.R` — main entry point for analyses  
- `Execute/Control[1_1, 1_2, 1_3, m1, m2, m3].R` — adjust parameters (e.g., pLDDT threshold, dataset type)


## Environment setup

This project uses `renv` to manage the R environment and ensure reproducibility.
The file `renv.lock` records the exact versions of all R packages used when the analyses were run.

To recreate the project environment, run the following commands from the root of the repository:

```r
install.packages("renv")
renv::restore()
```
This will automatically install all required packages and reproduce the exact package versions used in the analyses.

The package versions used in the project are recorded in `renv.lock`.

## How to run

All analyses in this repository are launched from the `Execute/` directory. 
The main entry point is:

- `Execute/RunAll.R`

Ensure your working directory is set to the **root of the repository** before running this script.

`RunAll.R` is organized into analysis blocks. Each block:

1. Clears the R workspace to ensure reproducibility
2. Sources a corresponding control file (when available)
3. Sources a logging and execution script that runs the analysis and writes outputs to `Results/` (and logs to `Log/`)


### Recommended workflow

1. Open `Execute/RunAll.R`.
2. Identify the analysis block(s) you want to run (e.g., Analysis 1.1, 1.2, 1.3, m1–m3, matching).
3. **Adjust the corresponding control file(s)** in `Execute/` (e.g., `Control1_1.R`, `Control_m2.R`) if you need to change thresholds, dataset types, or other parameters available.
4. Run only the block(s) you need.
